Which of my Transient Type Checks are not (Almost) Free?

### 2019-09-11 paper.tex
Minor edits in introduction
Signed-off-by: Stefan Marr <git@stefan-marr.de>

Unfortunately most gradual systems with run-time semantics (as opposed to type erasure as in TypeScript) typically impose significant run-time performance overheads. This has lead to a significant body of research to develop techniques to optimise gradual typing \citep{Vitousek2017,Muehlboeck2017,Bauman2017,Richards2017,Greenman2018}.

This has also lead to a technique to evaluate the performance of gradual typing, such as the so called so-called ``Takikawa'' protocol \cite{Takikawa2016,Greenman2019jfp,vitousek-transient-arXive-2019}. The Takikawa protocol was created to measure the run-time cost of gradual typing by testing various configurations of typed/untyped code. This approach was designed to investigate the the performance effect of the amount of typed vs untyped code, in particular it shows that how simply adding more type annotations does not always produce a uniform effect on performance. Here we adapt their approach in order to identify individual type annotations that may be responsible for performance effects.

>>>>

Unfortunately most gradual systems with run-time semantics, as opposed to type erasure as in TypeScript, impose significant run-time performance overheads. This has lead to a significant body of research to develop techniques to optimise gradual typing \citep{Vitousek2017,Muehlboeck2017,Bauman2017,Richards2017,Greenman2018}.

This has also lead to a technique to evaluate the performance of gradual typing, such as the so called so-called ``Takikawa'' protocol \cite{Takikawa2016,Greenman2019jfp,vitousek-transient-arXive-2019}. The Takikawa protocol was created to measure the run-time cost of gradual typing by testing various configurations of typed/untyped code. This approach was designed to characterise how the amount of typed and untyped code influences performance.
In particular it shows that how simply adding more type annotations does not always produce a uniform effect on performance. Here we adapt their approach in order to identify individual type annotations that may be responsible for performance effects.
